Awareness and Russell's Epistemology

### 2011-01-27 paper.tex
Some new boilerplate

%%%%%%%%%% Start TeXmacs macros
\newcommand{\mathbbm}{\mathbb}
\newcommand{\assign}{:=}
\newcommand{\nin}{\not\in}
\newcommand{\tmem}[1]{{\em #1\/}}
\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmstrong}[1]{\textbf{#1}}
\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
\newcommand{\tmtextup}[1]{{\upshape{#1}}}
\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
\definecolor{grey}{rgb}{0.75,0.75,0.75}
\definecolor{orange}{rgb}{1.0,0.5,0.5}
\definecolor{brown}{rgb}{0.5,0.25,0.0}
\definecolor{pink}{rgb}{1.0,0.5,0.5}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
%%%%%%%%%% End TeXmacs macros

\begin{document}

@@

\begin{abstract}
  In this essay, we show that awareness logic is suitable for
  formal modeling of Bertrand Russell's theory of knowledge,
  originally developed in \cite{russell_problems_1936}.  This is done
  by introducing a novel property to the semantics of 
  awareness logics. 
  We present a variety of sound and complete awareness
  logics compatible which exhibit this property.
\end{abstract}
\todo{This abstract isn't flowery enough.  Lookup PhD comics
  ``Abstract madlibs'' and use that as a template.}

\listoftodos

\section{Introduction}
\label{intro}
\input{introduction.tex}

>>>>

%%%%%%%%%% Start TeXmacs macros
\newcommand{\mathbbm}{\mathbb}
\newcommand{\assign}{:=}
\newcommand{\nin}{\not\in}
\newcommand{\tmem}[1]{{\em #1\/}}
\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmstrong}[1]{\textbf{#1}}
\newcommand{\tmtextbf}[1]{{\bfseries{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextsf}[1]{{\sffamily{#1}}}
\newcommand{\tmtextup}[1]{{\upshape{#1}}}
\newenvironment{descriptioncompact}{\begin{description} }{\end{description}}
\newenvironment{descriptiondash}{\begin{description} }{\end{description}}
\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
\newenvironment{enumerateroman}{\begin{enumerate}[i.] }{\end{enumerate}}
\newenvironment{itemizedot}{\begin{itemize} \renewcommand{\labelitemi}{$\bullet$}\renewcommand{\labelitemii}{$\bullet$}\renewcommand{\labelitemiii}{$\bullet$}\renewcommand{\labelitemiv}{$\bullet$}}{\end{itemize}}
\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
\definecolor{grey}{rgb}{0.75,0.75,0.75}
\definecolor{orange}{rgb}{1.0,0.5,0.5}
\definecolor{brown}{rgb}{0.5,0.25,0.0}
\definecolor{pink}{rgb}{1.0,0.5,0.5}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
%%%%%%%%%% End TeXmacs macros

\newcommand{\PP}{\circlearrowleft}
\newcommand{\nmodels}{\nvDash}
\begin{document}

@@

\begin{abstract}
This paper presents a novel approach to formulating epistemic directly
in terms of logical inference.  Using awareness logic, $\Box_X \phi$ is
taken to literally mean ``it follows from formulae $X$ is explicitly aware of
that $\phi$''.  This is done by incorporating logic into the semantics
of awareness logic.  Our approach corresponds closely to the framework
for epistemology proposed by Bertrand
Russell\cite{russell_problems_1936}, and illustrates that
objections provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
the proposed interpretation of epistemic logic should be considered invalid.
\end{abstract}

\listoftodos
\section{Introduction}
\label{intro}
\input{introduction.tex}
